## Puducherry

Basic descriptive statistics about the data. And sanity checks.

```{r load_data}
puducherry <- readr::read_csv("puducherry.csv")
```

Number of rows:

```{r nrows}
nrow(puducherry)
```

Unique Values in Sex:

```{r unique_vals_in_sex}
# Unique values in sex
table(puducherry$sex)
```

Summary of Age:

```{r age}
# Age
summary(puducherry$age)
```

Check if 0 and missing age is from problem in the electoral roll:

```{r zero_missing_age}
puducherry[which(puducherry$age == 1), c("id", "filename")]
```

No. of characters in ID:
```{r length_of_id}
# Length of ID
table(nchar(puducherry$id))
```

Number of characters in pin code:

```{r nchar_pincode}
table(nchar(puducherry$pin_code))
```

Are IDs duplicated?

```{r duplicate_ids}
length(unique(puducherry$id))
nrow(puducherry)
```

```{r total_electors}
# Net electors
sum(with(puducherry, rowSums(cbind(net_electors_male, net_electors_female), na.rm = T) == net_electors_total), na.rm = T)
nrow(puducherry)
```

No. of characters in elector name and checks around that:
```{r checks_elector_name_size}
## Checks that succeeded
table(nchar(puducherry$elector_name))
puducherry[which(nchar(puducherry$elector_name) < 4), c("id", "filename")]
```

Does district have a number?
```{r district_number}
sum(grepl('[0-9]', puducherry$district))
```

Basic admin. units:
```{r police_station_mandal_district_main_town}
table(puducherry$parl_constituency)
table(puducherry$ac_name)

table(puducherry$police_station)
table(puducherry$mandal)
table(puducherry$district)
table(puducherry$main_town)
```
